\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-29 flux.tex
Minor revision.

Further work characterizing antigenic evolution in the human influenza virus may eventually prove to be crucial in improving vaccine strain selection.

>>>>

A deeper understanding of the process of antigenic evolution in the human influenza virus may eventually prove to be crucial in improving vaccine strain selection.
